\documentclass[11pt,a4paper]{article}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage[margin=2.5cm]{geometry}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}

\begin{document}
\thispagestyle{empty}

\begin{flushright}
Wojciech Mocek\\
Rybnik, Poland\\
+48 667 295 982\\
\href{mailto:mocek.w@gmail.com}{mocek.w@gmail.com}\\
\href{https://linkedin.com/in/wmocek}{linkedin.com/in/wmocek}\\[0.5em]
\today
\end{flushright}

\vspace{1em}

\noindent Hiring Committee\\
International School of Krakow\\
Krakow, Poland

\vspace{1em}

\noindent\textbf{Re: Letter of Interest -- On-Call Substitute Teacher Position}

\vspace{1em}

Dear Hiring Committee at the International School of Krakow,

I am writing to express my strong interest in the On-Call Substitute Teacher position at the International School of Krakow. With over three decades of dedication to mathematics education and a profound commitment to child-centered learning, I am eager to contribute to ISK's mission of creating a secure, nurturing, and intellectually inspiring environment for students.

As an experienced educator with full legal eligibility to work in Poland and fluency in English, I meet all prerequisites for this position. My professional background includes 32+ years of teaching mathematics at university and secondary levels, working with students across diverse age groups and ability levels. I have consistently fostered curiosity, analytical thinking, resilience, and mutual respect in every classroom setting. My approach emphasizes not only academic excellence but also the development of each student's confidence and love of learning.

While I am based in Rybnik, I am well-positioned to serve ISK reliably, as I am located just 1.5 hours from Krakow with excellent transportation access. I bring the flexibility, dependability, and strong sense of professional responsibility that are essential for effective substitute teaching. My extensive teaching experience has equipped me to adapt quickly to different classroom environments, maintain continuity in students' learning, and uphold the highest standards of educational practice.

I am particularly drawn to ISK's unwavering dedication to safeguarding and promoting the welfare of every student. This commitment resonates deeply with my own professional values, which center on empathy, integrity, inclusivity, and the belief that every child deserves a safe and supportive learning environment. I understand the critical importance of maintaining vigilance and adhering to international safeguarding standards, and I am fully prepared to contribute to a culture of care and protection at ISK.

My background also includes international academic experience, having worked as a research assistant at institutions in the United States (Georgia Institute of Technology, Medical University of South Carolina) and Spain (Universitat Autònoma de Barcelona). This exposure to diverse educational contexts has strengthened my cross-cultural awareness and my ability to connect with students from varied backgrounds—qualities that align well with ISK's international community.

I would welcome the opportunity to discuss how my experience, dedication, and values can support your school community as part of the substitute teaching team. Thank you very much for considering my application. I look forward to the possibility of contributing to the outstanding educational environment at the International School of Krakow.

\vspace{1em}

Sincerely,

\vspace{2em}

Wojciech Mocek

\end{document}
